\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-20 paper.tex
update in abstract

\subsection*{Abstract}
Testing distributed storage systems is challenging due to multiple sources of nondeterminism. Conventional testing techniques, such as unit and stress testing, are ineffective in preventing serious but subtle bugs from reaching production. Formal techniques, such as TLA+, can only verify high-level specifications of systems at the level of logic-based models, and fall short of checking the actual executable code. In this paper, we present a new methodology for testing production distributed systems. Our approach applies systematic testing techniques to thoroughly check that the executable code adheres to its high-level specifications, which significantly improves coverage of important system behaviors.

>>>>

\subsection*{Abstract}
Testing distributed storage systems is challenging due to multiple sources of nondeterminism. Conventional testing techniques, such as unit and stress testing, are ineffective in preventing serious but subtle bugs from reaching production. Formal techniques, such as TLA+, can only verify high-level specifications of systems at the level of logic-based models, and fall short of checking the actual executable code. In this paper, we present a new methodology for testing distributed storage systems. Our approach applies advanced systematic testing techniques to thoroughly check that the executable code adheres to its high-level specifications, which significantly improves coverage of important system behaviors.
